---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# add2snippets

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/199655626.svg)](https://zenodo.org/badge/latestdoi/199655626)
<!-- badges: end -->

The goal of add2snippets is to help add useful R snippets and avoid wasting time on writing duplicated codes. There are similar packages like [Selected_Code_To_Snippet](https://github.com/Timag/Selected_Code_To_Snippet). Further more information, see
[notes](https://jiaxiangbu.github.io/learn_rstudioapi/analysis/rstudio-and-api-learning-notes.html#snippets).

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JiaxiangBU/add2snippets")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(add2snippets)
## basic example code
```

```{r}
add_uml(open.r.snippets = FALSE)
```

***

`r add2pkg::add_disclaimer()`
